\documentclass[11pt,a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[explicit]{titlesec}
\usepackage{fontawesome}
\usepackage{xcolor}
% \usepackage{fontspec} % Required for custom fonts - NEED XELATEX OR LUALATEX
\usepackage{graphicx}

% CV INSPIRATION:
% https://www.cs.utoronto.ca/~hinton/fullcv14.pdf
% https://tacocohen.wordpress.com/wp-content/uploads/2024/09/cv_taco_cohen.pdf
% https://www.eduardofonseca.net/assets/cv/CV_Eduardo_Fonseca_short.pdf
% https://tristandeleu.github.io/assets/pdf/cv.pdf

% You can change many parts of this CV, make different versions in different languages or make an extensive version, etc.

% Colors
\definecolor{linkcolor}{RGB}{0,0,139}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor
}

% Font setup
\setmainfont{EB Garamond} % Set main font to EB Garamond or another serif font

% Custom section formatting with blue titles and lines
\titleformat{\section}
  {\Large\bfseries\color{linkcolor}} % Title text in blue
  {} % No prefix
  {0em} % Spacing between title and line
  {#1\textcolor{linkcolor}{\hrulefill}} % Blue line after title

% Custom commands
\newcommand{\link}[2]{\href{#1}{#2}}

\begin{document}
\sloppy

% GENERAL INFORMATION
\noindent
\begin{minipage}[t]{0.5\textwidth}
    \Huge \textbf{Huang Jue He} \\[6pt]
    \large \textit{Curriculum Vitae}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \link{mailto:huangjuehe@gmail.com}{huangjuehe@gmail.com} \\
    \link{mailto:hhehuang79@alumnes.ub.edu}{hhehuang79@alumnes.ub.edu} \\
    655032091\\
    \link{https://hjh.github.io/}{hjh.github.io} \\
\end{minipage}

% INTRODUCTION
\section*{About me}
Mathematics student at the University of Barcelona.\\
I define myself as an organized and detail-oriented person, eager to learn and a team worker.\\
Experience with basic computer applications, databases, algorithms and data structures, web scrapers and web development.
\begin{itemize}[label=-]
    \item Interest in mathematical foundations of AI, financial mathematics, algorithmic trading.
    \item Experience in customer service and fashion retail.
\end{itemize}

% EDUCATION SECTION - institution & degree interchangeable priority
\section*{Education}

\href{https://mat.ub.edu/graumatematiques/}{\textbf{Universitat de Barcelona}} \hfill 2025 - Present \\ 
Bachelor of Science in Mathematics
\begin{itemize}[label=-]
    %\item Thesis: \textit{On Deep Multiscale Recurrent Neural Networks}
    %\\ Advisor: Prof. José Manuel García Rodríguez
    \item Computer Science Track: Artificial Intelligence, Software Engineering...
\end{itemize}

\noindent
\href{https://fi.upm.es/?id=gradoingenieriainformatica}{\textbf{Universidad Politécnica de Madrid}} \hfill 2018-2021 (Withdrawn) \\
Bachelor of Engineering in Computer Science \& Engineering
\begin{itemize}[label=-]
    %\item Thesis: \textit{On Deep Multiscale Recurrent Neural Networks}
    %\\ Advisor: Prof. José Manuel García Rodríguez
    \item Relevant coursework: \textit{Advanced Programming, Operations Research, Algorithms and Data Structures...}
\end{itemize}

% PROFESSIONAL EXPERIENCE - Newest on top
\section*{Professional Experience}
\noindent
\textbf{UNIQLO Gran Vía}, Madrid \hfill February 2025 - September 2025 \\
\textit{Sales Assistant}
    \begin{itemize}[label=-,itemsep=0pt]
    	\item Stock, shop floor inventory \& KPIs control.
	\item Customer service, product advice.
        \item Cleaning and organization of in-store displays for visual merchandising.
    \end{itemize}

\noindent
\textbf{El Corte Inglés Castellana}, Madrid \hfill October 2024 - February 2025 \\
International Customer Service
    \begin{itemize}[label=-]
        \item Multilingual support for international customers for tax-free process \& assistance with various matters.
    \end{itemize}

\noindent
\textbf{Self-Employed}, Madrid \hfill 2020 - 2023\\
Developer \& Seller
    \begin{itemize}[label=-]
        \item Development in Python and JS of APIs, web scrapers \& auto-checkout programs with secure payment processing (Adyen) \& WAF bypassing of PerimeterX, Cloudflare, Akamai.
        \item Management of five-figure valued inventory \& basic accounting.
    \end{itemize}

\noindent
\textbf{Max Shop}, Torrevieja \hfill 2020\\
\hspace{10pt}Sales Associate\\

\noindent
\textbf{Merca Centro Chiclana}, Cádiz \hfill 2018 - September 2019\\
\hspace{10pt}Sales Associate 
    \begin{itemize}[label=-,itemsep=0pt]
        \item Cashier, invoices, refunds or exchanges.
        \item Management and restocking of store inventory.
    \end{itemize}

\noindent
\textbf{Restaurante WOK Bahia Sur}, Cádiz \hfill June 2017 - September 2017\\
\hspace{10pt}Waiter 
    \begin{itemize}[label=-,itemsep=0pt]
        \item Preparation and cleaning of the establishment.
        \item Mastery of established processes and procedures.
    \end{itemize}


% EXTRACURRICULAR SECTION
\section*{Extracurriculars \& Services}
\textbf{Student Representative}, Universidad Politécnica de Madrid \hfill 2019,2020

% PRIZE & AWARDS SECTION
%\section*{Awards and scholarships}
%\textbf{Excellence Award}, \textit{C\$ 2500}, Université de Montréal \hfill 2027

% SKILLS & OTHERS SECTIONS
\section*{Skills}
\textbf{Programming languages}: Proficient in Java, Python, C, SQL. Basic knowledge of JavaScript, R, Bash.\\[2pt]
\textbf{Technologies}: MATLAB, HTML \& CSS, \LaTeX, pandas, matplotlib.\\[2pt]
\textbf{Languages}: Spanish, Catalan, English, Chinese (Bilingual/native level). French (Intermediate/Advanced). Russian (Beginner).\\[2pt]
\textbf{Personal interests}: Geography, history, climbing.\\[5pt]

% PUBLICATIONS & ARTICLES SECTION
%\section*{Publications}
%\begin{enumerate}[label={[\arabic*]}, leftmargin=1.5em]
%    \item \textbf{Svanberg, E.}, Cui, C., Latter, H. (2022) \href{https://link-to-article.com}{Wavelike nature of the vertical shear instability in global protoplanetary disks}. \textit{MNRAS} 
    
%    \item \textbf{Svanberg, E.} (2022) \href{https://link-to-article.com}{Higher-order time derivative theories and the Ostrogradsky ghost}. \textit{Preprint} 

%    \item \textbf{He, H} (2025) \href{https://link-to-article.com}{Science Research Publication}. \textit{Science Magazine} 
    
%    \item \textbf{He, H} (2026) \href{https://link-to-article.com}{Quantitative Research article}. \textit{Quant Magazine} 

%\end{enumerate}

\vfill
\noindent
\small version: October 2025

\end{document}
